```{=latex}
\pagenumbering{roman}
```

```{r include=FALSE}
library(knitr)
```


`r if (knitr:::is_html_output()) '
# Declaration{-}
'`
`r if (knitr:::is_latex_output()) '
# Declaration {.unlisted .unnumbered}
'`

I, Yifan Wu, hereby declare that this dissertation is all my own original work and that all sources have been acknowledged. It is 11,678 words in length.

Yifan Wu, 24th August 2025

`r if (knitr:::is_html_output()) '
# Acknowledgements{-}
'`
`r if (knitr:::is_latex_output()) '
# Acknowledgements {.unlisted .unnumbered}
'`
The stream of time carries one along, and in the blink of an eye, a year has flowed by. On the day I landed at Heathrow, the air held an unfamiliar dampness, yet now this city has become a soft, warm hue in my memory. My thesis has reached the acknowledgements, and my student days are now but a footnote.

In my undergraduate dissertation, I never wrote a proper acknowledgement—a small regret that has stayed with me ever since. Here, I wish to make amends. Out of personal sentiment, I do not want this acknowledgement to be formal or cold; nor do I want to worry too much about grammar or precision. I hope it can be gentle, tender, and sincere. I hope it may stand as the beating, living heart of feeling within a text otherwise forged by reason.

First, I wish to thank Duncan, my supervisor. He is witty, conscientious, looks splendid in a shirt, and when he smiles, he bears a gentle resemblance to a kind lead in a British drama. In his CASA0003 lectures, data ceased to be arid figures; instead, it was dissected, deconstructed, and reassembled into visual poetry. He lectured without pedantry, as effortlessly as sharing an inspiration over coffee. Over these thesis-writing months, whether meeting in person or online, we discuss ideas or perplexities, he remained ever composed—leaving suggestions in my paper, annotating thoughts in emails. I cannot express my gratitude sufficiently, Dear Duncan. It is he who has kept alive my passion for knowledge.

My thanks also extend to every teacher encountered this year. And CASA—this place feels to me like an endless academic gathering in London.

My deepest gratitude goes to my parents and family far away. If studying abroad was a blueprint I drew myself, every brick was laid by their silent support. Financially and emotionally, they never hesitated. They made me believe: just keep moving forward, for behind you shine a light that will never go out. During those transcontinental video calls, their faces blurred by low resolution, their reminders always the same: ‘Eat properly,’ ‘Get enough sleep.’ They said even at three in the morning, their phones would always be open for me. They taught me to live earnestly, yet never forget to look up at the path ahead. I love you both, in a way I couldn't articulate before, but now wish to write down earnestly.

And my friends—each one of them, real and solid, standing beside me in the photographs. What I mean is, the camera is my eyes. They’re the ones who painted hues onto London’s grey palette. I never imagined meeting so many gentle new companions during my postgraduate years. My circle has always been small, almost unchanging. 

Thank you, dear Xi (Xinyi Zeng), for always appearing when I hit rock bottom, catching me and holding me up. We wandered London's vintage shops and cafés, we drank heartily in Paris's bustling night bars, we ran through Greenwich's sunshine and rain. Thank you for constantly feeding me all sorts of delicious treats and fun things; your cooking is so good I could polish off three bowls of rice in one go. By the way, I've already finished the book you recommended. 

Thank you, dear Weng (Qican Weng), for rowing with me in the park during the May Day holiday, for photographing under the full moon and the setting sun at Tower Bridge, and for battling through our thesis deadlines together at SC until sunrise. 

Thank you, dear Han (Shuhan Zhang) and Yue (Xinyue Hu) – it's almost six years since we met each other. Continuing our postgraduate studies at the same university and supporting each other is an immense blessing. See you back home.

Thank you, dear Yun (Yanyun Xu), for bringing me to KCL to study together, for sunbathing in Finsbury Park together. I'll never forget how, after we parted at Holborn station, you turned back—just to find me, only to hug me and tell me to take care.

Thank you, dear Cheng (Shiyu Cheng), for seeing my first live opera together, for visiting that terrifying murder exhibition, for strolling through the streets on fireworks nights – those were the happiest times of my study abroad. And nice to meet u.

Thank you, dear Qiu (Yue Qiu) and Bababoi (Borui Wang). Our combined efforts ensured CASA0003 delivered a remarkably powerful presentation and score. You two will always be my little pistachios, the cutest sparks of joy.

Thank you, dear Ssie (Tingxuan Shi), for taking me out onto the streets of London for the very first time. We snapped photos beneath the neon signs of Soho and sipped drinks at Swift's. You are like a little sun, radiating warmth and enthusiasm. You are my very first friend in London.

Thank you, dear Qi (Liu Zengqi), for always worrying about me and fussing over me. You would message me the moment I showed the slightest hint of low spirits, inviting me over for dinner—though your kitchen really was sweltering. I still remember that one time we crossed the road near Waterstones, you said to me, ‘Thank you.’ You might not recall it, but I do. You taught me that in any relationship, we must have the courage to express ourselves—just as I am doing now. 

My friends are the soundtrack to my memories—sometimes boisterous, sometimes serene, yet ever-present. Thank you for crossing paths with me, and, I love you all.

Finally, I wish to gently embrace that past and present self of mine. Thank you for weathering two major illnesses during the application period. Thank you for rebuilding yourself anew in a foreign land. Thank you for not fleeing amidst the thick fog of multifaceted pressures. Thank you, Yifan Wu. And, I love you so much.

May it be that this stretch of time never fades, like London's everlasting sunset, forever beckoning to me with gentle, radiant warmth.

May it be that the me of years hence, standing on the other shore of time, still clearly sees this figure: bent over a desk by the library window, lost in thought by the Thames, weeping in the dead of night yet never giving up.

**May I always recognise her,**

**understand her,**

**and walk towards her.** 

**Steadily, always.**



```{=latex}
% Trigger ToC creation in LaTeX
\setcounter{tocdepth}{3}
\tableofcontents
\listoffigures
\listoftables
```

`r if (knitr:::is_html_output()) '
# Abbreviations{-}
'`
`r if (knitr:::is_latex_output()) '
# Abbreviations {.unlisted .unnumbered}
'`

```{r abbreviations, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(readxl)
library(fs)
library(here)

read_excel(here("tables", "abbreviations.xlsx"))%>%
  arrange(Term) %>% # i.e. alphabetical order by Term
  knitr::kable(booktabs = TRUE)%>% # booktab = T gives us a pretty APA-ish table
  kable_styling(position = "center")%>%
    row_spec(.,
  row=0,
  bold = TRUE)
```

