
```{=latex}
\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography
```
# Appendix {.unnumbered}

## Appendix A Key Parameter Summary {-}

```{=latex}
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
```

* **Coordinate system & traffic direction**:

  `crs_metric='EPSG:27700'` / `crs_output='EPSG:27700'`; `right_hand_traffic=True`.

* **Sidepath buffer**:

  `sidepath_buffer_size=22`; `sidepath_buffer_distance=100`.

* **Default one-way setting**:

  `default_oneway_cycle_lane='yes'`; `default_oneway_cycle_track='yes'`.

* **Default road width (m)**:

  `primary=17`, `secondary=15`, `tertiary=13`, `residential=11`, `living_street=6`, etc.

* **Default facility/parking width (m)**:

  Motor vehicles 3.2, buses 4.5, bicycles 1.4, pedestrians 2.2, rail 4.5, vertical 5.0.

* **Default surface layers**:

  `default_highway_surface_dict`, `default_cycleway_surface_*`, `default_track_surface_dict`.

* **Base components**:

  `base_index_dict` (path/track/lanes/bus/bicycle/shared...).

* **Road class / speed limit factors**:

  `highway_factor_dict`, `maxspeed_factor_dict`.

* **Factor weighting**:

  `highway_factor_dict_weights` (higher weight for mixed with motor traffic, lower for segregated facilities).

* **Surface / smoothness factors**:

  `surface_factor_dict`, `smoothness_factor_dict`.

* **Data completeness factors**:

  `data_incompleteness_dict` (`surface=30`, `width=25`, etc.).

* **Road classes prohibited for cycling**:

  `cycling_highway_prohibition_list` (`motorway`, `trunk`, etc.).


\clearpage

```{r, results='asis', echo=FALSE}
if (knitr:::is_latex_output()) {
  cat("## Appendix B  Research log {.unlisted .unnumbered}\n")
} else if (knitr:::is_html_output()) {
  cat("## Appendix B  Research log {-}\n")
}
```

```{r researchlog, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(readxl)
library(fs)
library(here)

read_excel(here("tables","research_log.xlsx"))%>%
  knitr::kable(booktabs = TRUE)%>% # booktab = T gives us a pretty APA-ish table
  kable_styling(position = "center")%>%
  row_spec(.,
  row=0,
  bold = TRUE)
```

\clearpage

```{r, results='asis', echo=FALSE}
if (knitr:::is_latex_output()) {
  cat("## Appendix C  Research log {.unlisted .unnumbered}\n")
} else if (knitr:::is_html_output()) {
  cat("## Appendix C  Research log {-}\n")
}
```


```{=latex}
\addtocontents{toc}{\protect\setcounter{tocdepth}{3}}
\enddocument
```